%-------------------------
% Resume in Latex
% Author : Yogesh Patil
% Based off of: Aras Gungore's Template
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margin adjustment for optimal 1-page scannability
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - Modern Visual Hierarchy
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \small#2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING (UI: Identity Anchor) ----------
\begin{center}
    \textbf{\Huge \scshape Yogesh Patil} \\ \vspace{2pt}
    \small \textbf{DATA SCIENTIST} \\ \vspace{4pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:919579563457}{+91 9579563457} $|$
    \faEnvelope \hspace{.5pt} \href{mailto:yogeshpatil18999@gmail.com}{yogeshpatil18999@gmail.com} $|$
    \faLinkedin \hspace{.5pt} \href{https://www.linkedin.com/in/yogesh-patil-analyst/}{LinkedIn} $|$
    \faMapMarker \hspace{.5pt} Pune, IND
\end{center}

%----------- SKILLS (UX: Quick Extraction) -----------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{$\bullet$ Languages \& Tools:}{ SQL, Python, MS Excel, Power BI, Tableau, Hue, Hive, Impala, Oracle SQL Dev, PostgreSQL} \\ \vspace{2pt}
        \textbf{$\bullet$ Libraries \& Frameworks:}{ Scikit-learn, TensorFlow, Keras, Pandas, NumPy, Matplotlib, Seaborn} \\ \vspace{2pt}
        \textbf{$\bullet$ Concepts:}{ Supervised \& Unsupervised Learning, Logistic \& Linear Regression, Tree-Based Models, Clustering \& Segmentation, Statistical Modeling, Time Series Analysis \& Forecasting, Feature Engineering, A/B Testing, Data Preprocessing, Fraud Detection, Model Validation, KPI Design} \\ \vspace{2pt}
        \textbf{$\bullet$ Other:}{ Healthcare, Project Management, Communication, Problem Solving, Decision Making}
    }}
  \resumeSubHeadingListEnd

%----------- EXPERIENCE (UX: Achievement-Focused) -----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cotiviti}{Pune, IND}
      {Data Scientist}{Feb 2024 -- Present}
        \resumeItemListStart
            \resumeItem{Served as primary analytics liaison for two large U.S. insurance clients, leading end-to-end solutions and financial analysis to support strategic decision-making.}
            \resumeItem{Analyzed large-scale automated financial and claims datasets using SQL and Python to identify performance drivers supporting monthly invoicing and weekly operations.}
            \resumeItem{Applied statistical analysis, trend analysis, and segmentation to diagnose performance issues and inform data-driven recommendations for stakeholders.}
            \resumeItem{Built an end-to-end Python data pipeline integrating SQL and Excel to automate reconciliation workflows, resulting in \textbf{\textasciitilde\$2M (2024)} in annualized savings.}
            \resumeItem{Developed an anomaly detection framework leveraging time series analysis and unsupervised learning across historical windows to trigger automated alerts.}
            \resumeItem{Identified high-value claims with missing data and built \textbf{Power BI dashboards} to improve financial recovery through a monthly tracking process.}
        \resumeItemListEnd

    \resumeSubheading
      {Altimetrik}{Pune, IND}
      {Associate Analyst}{Sep 2021 -- Sep 2022}
        \resumeItemListStart
            \resumeItem{Led the initiative to enhance \textbf{Key Performance Indicators (KPIs)} within the TARA project, an extension of the ReportPortal platform.}
            \resumeItem{Applied unsupervised learning (K-Means clustering) to group workflows based on behavior and performance metrics to uncover inefficiencies.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- PROJECTS -----------
\section{Self Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {Graph-Based Anime Recommendation System $|$ \emph{\href{https://anime-recommender-wx0q.onrender.com/}{\color{blue}Live Link}}}{}
          \resumeItemListStart
            \resumeItem{Developed a recommendation system using feature engineering and K-Means clustering to deliver explainable recommendations using real-time MyAnimeList data.}
          \resumeItemListEnd
      \resumeProjectHeading
        {Preference App $|$ \emph{\href{https://guessing-game--yogeshpatil43.replit.app/}{\color{blue}Live Link}}}{}
          \resumeItemListStart
            \resumeItem{Created a full-stack application that analyzes user decision patterns to infer personality profiles using GPT-based reasoning.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%----------- EDUCATION -----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dr. D. Y. Patil Institute of Technology}{Pune, IND}
      {Bachelor of Engineering in Computer Science \& Engineering; \textbf{8.5 CGPA}}{2017 -- 2021}
  \resumeSubHeadingListEnd

%----------- AWARDS -----------
\section{Awards \& Recognition}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{$\bullet$ High Five Award (Cotiviti):}{ Annual Award; Recipient of 1 Monthly \& Quarterly Award for excellence in Data Science. $|$ \href{https://drive.google.com/file/d/1X9S02VJoPfQ28ysWWrs-yD8_JfB65dZ/view}{\color{blue}View Award}}
    }}
  \resumeSubHeadingListEnd

%----------- CERTIFICATES -----------
\section{Certificates}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{$\bullet$ Data Analytics:}{ Certified by SkilloVilla} \\ \vspace{2pt}
        \textbf{$\bullet$ Python for Data Analysis:}{ Certified by LinkedIn} \\ \vspace{2pt}
        \textbf{$\bullet$ Python 101, Visualization, Analysis:}{ Certified by CognitiveClass.AI}
    }}
  \resumeSubHeadingListEnd

\end{document}
