\documentclass[11pt]{article}        % set main text size
\usepackage[letterpaper,                % set paper size to letterpaper
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points
\usepackage[hidelinks]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt}

\begin{document}

% name
\centerline{\Huge YOGESH PATIL}

\vspace{5pt}

% contact information
\centerline{+91 9579563457 | \href{mailto:yogeshpatil18999@gmail.com}{yogeshpatil18999@gmail.com} | Pune, IND | \href{https://www.linkedin.com}{LinkedIn}}

\vspace{-10pt}

% skills section
\section*{Technical Skills}
\textbf{Languages \& Tools:} SQL, Python, MS Excel, Power BI, Tableau, Hue, Hive, Impala, Oracle SQL Dev, PostgreSQL \\
\textbf{Libraries/Frameworks:} Scikit-learn, TensorFlow, Keras, Pandas, NumPy, Matplotlib, Seaborn \\
\textbf{Concepts:} Supervised/Unsupervised Learning, Regression (Linear/Logistic), Tree-Based Models (Random Forest, XGBoost), Time Series Analysis, A/B Testing, Feature Engineering, Fraud Detection, KPI Design
\vspace{-6.5pt}

% experience section
\section*{Work Experience}

\textbf{Data Scientist,} Cotiviti -- Pune, IND \hfill Feb 2024 -- Present \\
\vspace{-9pt}
\begin{itemize}
  \item Serve as the primary analytics liaison for two large U.S. insurance clients, leading end-to-end solutions, reconciliation, and financial analysis to support strategic decision-making.
  \item Analyze large-scale automated financial and claims datasets using SQL (Hive, Impala) and Python to identify trends and anomalies for monthly invoicing and weekly operations.
  \item Apply statistical analysis, segmentation, and comparative analytics to diagnose performance issues and uncover savings opportunities for internal stakeholders.
  \item Built an end-to-end Python data pipeline integrating SQL and Excel, applying classification models and feature engineering to automate reconciliation, saving \textasciitilde\$2M (2024) annually.
  \item Developed an anomaly detection framework using time series analysis and unsupervised learning across rolling 4-week and 13-week windows to trigger proactive automated alerts.
  \item Identified high-value claims with incomplete data and implemented Power BI dashboards with a monthly tracking process, reducing outstanding claims and improving financial recovery.
\end{itemize}

\textbf{Associate Analyst,} Altimetrik -- Pune, IND \hfill Sep 2021 -- Sep 2022 \\
\vspace{-9pt}
\begin{itemize}
  \item Led the initiative to enhance Key Performance Indicators (KPIs) within the TARA project, a pivotal extension of the ReportPortal platform.
  \item Applied unsupervised learning (K-Means clustering) to group tasks and workflows based on performance metrics, uncovering inefficiencies and tailoring operational strategies.
\end{itemize}

\vspace{-10pt}

% projects section
\section*{Self Projects}

\textbf{Graph-Based Anime Recommendation System} \hfill Flask, Python \\
\vspace{-9pt}
\begin{itemize}
  \item Developed a recommendation engine using feature engineering, cosine similarity, and K-Means clustering.
  \item Leveraged real-time MyAnimeList data to deliver explainable, graph-based recommendations and statistical insights.
\end{itemize}

\textbf{Preference App} \hfill AI, Python \\
\vspace{-9pt}
\begin{itemize}
  \item Created a full-stack AI application that analyzes user decision patterns to infer personality profiles.
  \item Implemented GPT-based reasoning and structured data pipelines to deliver diverse, personalized recommendations.
\end{itemize}

\vspace{-10pt}

% education section
\section*{Education}
\textbf{Dr. D. Y. Patil Institute of Technology} -- B.E. in Computer Science \& Engineering \hfill 2017 -- 2021 \\
\textit{Result: 8.5 CGPA}

\vspace{-10pt}

% awards and certificates
\section*{Awards \& Certificates}
\begin{itemize}
    \item \textbf{High Five Award (Cotiviti):} Annual Award; recipient of 1 Monthly \& Quarterly Award.
    \item \textbf{Data Analytics:} Certified by SkilloVilla.
    \item \textbf{Python for Data Analysis:} LinkedIn Learning \& CognitiveClass.AI (Visualization, Analysis).
\end{itemize}

\end{document}
