%-------------------------
% Resume in Latex
% Author : Yogesh Patil
% Based off of: Aras Gungore's Template
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Yogesh Patil} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:919579563457}{+91 9579563457}
    $|$
    \faAt \hspace{.5pt} \href{mailto:yogeshpatil18999@gmail.com}{yogeshpatil18999@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/yogesh-patil-analyst/}{LinkedIn}
    $|$
    \faMapMarker \hspace{.5pt} Pune, IND
\end{center}


%----------- SKILLS -----------

\section{Technical Skills}
  \resumeSubHeadingListStart
    \begin{itemize}[leftmargin=0.15in, label={\tiny$\bullet$}, topsep=0pt, partopsep=0pt, itemsep=3pt]
        \item \small{\textbf{Languages \& Tools:}{ SQL, Python, MS Excel, Power BI, Tableau, Hue, Hive, Impala, Oracle SQL Dev, PostgreSQL}}
        \item \small{\textbf{Libraries \& Frameworks:}{ Scikit-learn, TensorFlow, Keras, Pandas, NumPy, Matplotlib, Seaborn}}
        \item \small{\textbf{Concepts:}{ Supervised/Unsupervised Learning, Regression, Tree-Based Models, Time Series, A/B Testing, Feature Engineering}}
        \item \small{\textbf{Other:}{ Healthcare, Project Management, Communication, Problem Solving, Decision Making}}
    \end{itemize}
  \resumeSubHeadingListEnd


%----------- EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cotiviti}{Pune, IND}
      {Data Scientist}{Feb 2024 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Served as primary analytics liaison for two large U.S. insurance clients, leading end-to-end solutions and financial analysis to support strategic decision-making and profitability initiatives.}
            \resumeItem{Analyzed large-scale automated financial and claims datasets using SQL and Python to identify performance drivers supporting monthly invoicing and weekly operations.}
            \resumeItem{Applied statistical analysis, trend analysis, and segmentation to diagnose performance issues and inform data-driven recommendations for stakeholders.}
            \resumeItem{Built an end-to-end Python data pipeline integrating SQL and Excel to automate reconciliation workflows, resulting in \textasciitilde\$2M (2024) in annualized savings.}
            \resumeItem{Developed an anomaly detection framework leveraging time series analysis and unsupervised learning across rolling 4-week and 13-week historical windows to trigger automated alerts.}
            \resumeItem{Identified high-value claims with missing data and built Power BI dashboards to improve financial recovery through a monthly tracking process.}
        \resumeItemListEnd

    \resumeSubheading
      {Altimetrik}{Pune, IND}
      {Associate Analyst}{Sep 2021 \textbf{--} Sep 2022}
        \resumeItemListStart
            \resumeItem{Led the initiative to enhance Key Performance Indicators (KPIs) within the TARA project, an extension of the ReportPortal platform.}
            \resumeItem{Applied unsupervised learning (K-Means clustering) to group workflows based on behavior and performance metrics to uncover inefficiencies.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd


%----------- PROJECTS -----------

\section{Self Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{Graph-Based Anime Recommendation System} $|$ \emph{\href{https://anime-recommender-wx0q.onrender.com/}{\color{blue}Live Link}}}{}
          \resumeItemListStart
            \resumeItem{Developed a recommendation system using feature engineering and K-Means clustering to deliver explainable recommendations using real-time MyAnimeList data.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Preference App} $|$ \emph{\href{https://guessing-game--yogeshpatil43.replit.app/}{\color{blue}Live Link}}}{}
          \resumeItemListStart
            \resumeItem{Created a full-stack application that analyzes user decision patterns to infer personality profiles using GPT-based reasoning.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd


%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Dr. D. Y. Patil Institute of Technology}{Pune, IND}
      {Bachelor of Engineering in Computer Science \& Engineering; \textbf{8.5 CGPA}}{2017 \textbf{--} 2021}
    
  \resumeSubHeadingListEnd


%----------- AWARDS -----------

\section{Awards \& Recognition}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{High Five Award (Cotiviti):}{ Annual Award; Recipient of 1 Monthly \& Quarterly Award for excellence in Data Science. $|$ \href{https://drive.google.com/file/d/1X9S02VJoPfQ28ysWWrs-yD8_JfB65dZ/view}{\color{blue}View Award}}
    }}
  \resumeSubHeadingListEnd


%----------- CERTIFICATES -----------

\section{Certificates}
  \resumeSubHeadingListStart
    \begin{itemize}[leftmargin=0.15in, label={\tiny$\bullet$}, topsep=0pt, partopsep=0pt, itemsep=3pt]
        \item \small{\textbf{Data Analytics:}{ Certified by SkilloVilla}}
        \item \small{\textbf{Python for Data Analysis:}{ Certified by LinkedIn}}
        \item \small{\textbf{Python 101, Visualization, Analysis:}{ Certified by CognitiveClass.AI}}
    \end{itemize}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
